### 2014-11-07 D1-3.tex
Added abstract. Updated Graphics.

\LGversion{12}
%\LGstaffmonths{Resources spent on the deliverable}

@@

% \TODO{Add abstract}

%  This deliverable describes the mobile sensor mining component.
%  Along with this document we supply the source code of the
%  components, documentation (javadoc), and pre-compiled packages for
%  direct installation and testing on mobile devices.

}

@@

% add a \LGaddhistory{version}{date}{reason}{revised by} for each new
% version
\begin{LGhistory}
\LGaddhistory{01}{2014-07-17}{Outline}{Heinrich Hartmann}

\end{LGhistory}

@@

\LGaddauthor{UKob}{Christoph Schaefer}{+49 261 287 2786 }%
{+49 261 287 100 2786}{\small chrisschaefer@uni-koblenz.de}

@@

\LGaddauthorNoPhone{BIZ}{Maite de Arana Agiretxe}%
{\small komunikazioa.tekniko1@biscaytik.eu}

@@

\LGaddabbreviation{\textbf{ALC}}
{Attribute Language with Complement}

@@

\LGaddabbreviation{\textbf{GeSA}}
{Geographical Semantic Analysis}

@@

@@

\LGaddabbreviation{\textbf{IEEE 802.11}}
{see WIFI, WLAN}

@@

\LGaddabbreviation{\textbf{RF-ID}}
{Radio-Frequency Identification}

\LGaddabbreviation{\textbf{SDCF}}
{Sensor Data Collection Framework}

@@

\LGaddabbreviation{\textbf{SVM}}
{Support Vector Machine}

\LGaddabbreviation{\textbf{TBox}}
{Terminological Box}

>>>>

\LGversion{9}
%\LGstaffmonths{Resources spent on the deliverable}

@@

This deliverable presents the privacy aware, server based reality
sensing infrastructure for Live+Gov applications.

We review the legal and ethical aspects of privacy and perform a
thorough security analysis of the Live+Gov applications. We identify
six main threats to privacy and make eight recommendations for
addressing these threats. These recommendations form the guidelines
for several privacy enhancements to our infrastructure which we
describe in this document.

Along with this document we supply the source code of the components,
documentation, and pre-compiled packages for direct installation.
}

@@

% add a \LGaddhistory{version}{date}{reason}{revised by} for each new
% version
\begin{LGhistory}
\LGaddhistory{01}{2014-07-17}{Added Outline of Deliverable}{Heinrich Hartmann}
\LGaddhistory{02}{2014-09-10}{Started IT Security Analysis}{Heinrich Hartmann}
\LGaddhistory{03}{2014-09-13}{Added Threat Table with Conflicts and Vulnearbilities}{Maximilian Meffert}
\LGaddhistory{03}{2014-09-15}{Description of IT Security Analysis}{Heinrich Hartmann}
\LGaddhistory{04}{2014-09-17}{Finished Description of Actors and Interests}{Maximilian Meffert}
\LGaddhistory{05}{2014-10-08}{Added chapter on Legal Aspects of Privacy}{Heinrich Hartmann}
\LGaddhistory{06}{2014-10-13}{Updated 7 Types of Privacy}{Heinrich Hartmann}
\LGaddhistory{07}{2014-10-15}{Updated IT Systems Description}{Heinrich Hartmann}
\LGaddhistory{08}{2014-10-21}{Added Implicit Privacy Type Violations}{Maximilian Meffert}
\LGaddhistory{09}{2014-10-25}{Added Description of Implementations}{Heinrich Hartmann}
\LGaddhistory{09}{2014-11-05}{Extended Threat Scenarios}{Heinrich Hartmann}
\LGaddhistory{09}{2014-11-07}{Added Introduction and Summary}{Heinrich Hartmann}
\end{LGhistory}

@@

%\LGaddauthor{UKob}{Christoph Schaefer}{+49 261 287 2786 }%
%{+49 261 287 100 2786}{\small chrisschaefer@uni-koblenz.de}

@@

%\LGaddauthorNoPhone{BIZ}{Maite de Arana Agiretxe}%
%{\small komunikazioa.tekniko1@biscaytik.eu}

@@

@@

@@

\LGaddabbreviation{\textbf{HAR}}
{Human Activity Recognition}

@@

@@

\LGaddabbreviation{\textbf{SLD}}
{Service Line Detection}

@@

### 2014-11-07 PrivacyProtection-2014-09-09.tex
Updated intro and summary.
Added abstract. Updated Graphics.

\section{Legal Aspects of Privacy}

@@

Based on the legal background presented here, we will derive the legal privacy requirements for our systems in \ref{sec:LEGAL_REQ}.

@@

\subsection{Defining Privacy}

@@

\subsection{The Seven Types of Privacy}

@@

We follow the Reference Model for IT Security Analysis as described in \cite{Grimm:ItSecRefModel}.
It supersedes earlier efforts by \cite{Avizienis}.

The reference model consists of a \emph{model} and a \emph{procedure}.
The model aims to organize common security terminology in a reasonable and practical way.
The procedure describes a method to analysis the IT system based on that model.
In this section we give a brief overview over the reference model.

@@

\section{Live+Gov Privacy Protection Analysis}

@@

In short, citizens are interested in
\begin{itemize}
\item convenience
\item legitimate use of personal data
\item physical wellbeing and health
\item financial profit
\item not being monitored.
\end{itemize}

%TODO:
- Nondisclosure of sensitive information to peers of the citizen.

>>>>

\section{Legal Aspects of Privacy} \label{sec:legal}

@@

@@

In this section we introduce our definition of privacy which as \emph{control over personal information} following C. Fried.
As this description is still on a very high level we go on to specify seven different privacy types in the next section.
These privacy types are then analyzed for their implications in the presence of different kinds of sensor data.

\subsection{Defining Privacy}\label{sec:ethics}

@@

\subsection{The Seven Types of Privacy}\label{sec:privacytypes}

@@

We follow the Reference Model for IT Security Analysis as described in \cite{Grimm:ItSecRefModel}.
It supersedes earlier efforts by e.g. \cite{Avizienis}.
The reference model consists of a \emph{model} and a \emph{procedure}.
The model aims to organize common security terminology in a reasonable and practical way.
The procedure describes a method to analysis the IT system based on that model.
In this section we give a brief overview over the reference model.

@@

\section{Live+Gov Privacy Protection Analysis}\label{sec:PPA}

@@

In short, citizens are interested in
\begin{itemize}
\item physical wellbeing and health
\item financial profit
\item convenience
\item legitimate use of personal data
\item non-disclosure of personal data to peers of the citizen
\item not being monitored.
\end{itemize}
